The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-08-15 src/tex/ms.tex
change e in formulas to exp Note that $e^{-1}$ and other simple powers of e are excluded from this
Add author contributions

\subsection{Spots \label{subsec:spots}}
Our star spot model is nearly entirely based on observations of the Sun. Sunspots can be resolved and are well-studied, whereas spots on other stars (especially non-solar-type stars) can only be observed indirectly. We therefore designed our spot model to mimic the behavior of sunspots but with parameterized values for spot temperature and lifetime that can be matched to observations of other stellar types and ages. On the Sun, spots have two regions shown in Figure \ref{fig:surface_map}: the dark, central umbra and the lighter, surrounding penumbra (a detailed review of sunspot behavior, including sizes and lifetimes, is described in \citet{solanki2003}). The spot area as a function of time is
\begin{equation}
    A(t) = \left\{
    \begin{array}{lr}
        A_0 e^{(t-t_0)/\tau}, & \text{if } t \leq t_0 \\
        A_0 - W(t-t_0), & \text{if } t > t_0
    \end{array}
    \right\}
\end{equation}
where $A_0$ is the maximum area reached, $t_0$ is the time of the maximum, $\tau$ is the exponential growth rate, and $W$ is the linear decay rate.

@@

>>>>

\subsection{Spots \label{subsec:spots}}
Our star spot model is nearly entirely based on observations of the Sun. Sunspots can be resolved and are well-studied, whereas spots on other stars (especially non-solar-type stars) can only be observed indirectly. We therefore designed our spot model to mimic the behavior of sunspots but with parameterized values for spot temperature and lifetime that can be matched to observations of other stellar types and ages. On the Sun, spots have two regions shown in Figure \ref{fig:surface_map}: the dark, central umbra and the lighter, surrounding penumbra (a detailed review of sunspot behavior, including sizes and lifetimes, is described in \citet{solanki2003}). The spot area as a function of time is
\begin{equation}
    A(t) = \left\{
    \begin{array}{lr}
        A_0 \exp{((t-t_0)/\tau)}, & \text{if } t \leq t_0 \\
        A_0 - W(t-t_0), & \text{if } t > t_0
    \end{array}
    \right\}
\end{equation}
where $A_0$ is the maximum area reached, $t_0$ is the time of the maximum, $\tau$ is the exponential growth rate, and $W$ is the linear decay rate.

@@

\section{Author Contributions} % see https://www.elsevier.com/researcher/author/policies-and-guidelines/credit-author-statement
{\bf Ted M Johnson:} Conceptualization, Methodology, Software, Writing - Original Draft
{\bf Cameron Kelahan:} Conceptualization, Methodology, Software, Writing - Review \& Editing
{\bf Avi M. Mandell:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review \& Editing, Supervision, Project administration, Funding acquisition
{\bf Ashraf Dhahbi:} Software
{\bf Tobi Hammond:} Software
{\bf Thomas Barclay:} Methodology, Software
{\bf Veselin B. Kostov:} Methodology
{\bf Geronimo L. Villanueva:} Resources, Writing - Review \& Editing, Supervision
